The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-07-26 paper.tex
more wip

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
interstellar medium (ISM). As photons from the CMB propagate through the intervening material
scattering, absorption, or additional emission can perturb the thermal CMB spectrum. In order to
measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free emission,
thermal dust emission) are a nuisance and careful modeling and removal of these components is
essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.

@@

At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
power spectrum of this perturbation is expected to be dominated by inhomogeneous heating of the IGM
at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
7$ where a detection can constrain the ionizing efficiency of early galaxies, UV photon
mean-free-path, and the minimum halo mass that can support star formation
\citep{2015MNRAS.449.4246G}.

Current 21 cm cosmology experiments can be broadly separated into two classes: global experiments
that are aiming to detect the spectral signature of the cosmologically redshifted 21 cm transition
after averaging over the entire sky, and power spectrum experiments that incorporate angular
information to attempt to measure the spatial power spectrum of cosmological 21 cm perturbations.
Ongoing global experiments include EDGES \citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA
\citep{todo_price_2017}, BIGHORNS \citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V},
and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B}.

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21 cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
\end{equation}
Therefore experiments conservatively need to achieve at least 4 orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
emission (after convolving with the instrumental response) is spectrally smooth. However the
low-frequency radio sky is composed of several components: galactic synchrotron emission, free-free
emission and absorption, supernova remnants, radio galaxies, and a confusing background of point
sources.  Ideally a foreground removal strategy should be informed by the measured spatial and
frequency structure of all foreground components. However, this possibility is limited by the
availability of suitable high-fidelity low-frequency sky maps on angular scales ranging from tens of
degrees to arcminutes.

The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is a data-driven
interpolation of various maps between 10 MHz and 100 GHz. However the majority of information
contained in the GSM is derived at higher frequencies where the majority of the input maps are from.
Below 408 MHz, the interpolation is largely driven by the Haslam 408 MHz map
\citep{1981A&A...100..209H, 1982A&AS...47....1H}.  At lower frequencies, free-free absorption and
synchrotron self-absorption becomes increasingly important and hence spectral indices derived at
higher frequencies need corrections at lower frequencies.

Recently a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio sources. Surveys that capture the diffuse emission include at 45 MHz, where
\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
Frequency Sky Survey \citet{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.

@@

\begin{deluxetable*}{ccccc}
    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
    \tablewidth{0pt}
    \tablehead{
        \colhead{\#} & \colhead{$\nu$ / MHz} & \colhead{$\Delta\nu$ / MHz} &
        \colhead{$\theta$ / arcmin} & \colhead{noise / Jy}
    }
    \startdata
        1 & 36.528 & 0.024 & & \\
        2 & 41.760 & 0.024 & & \\
        3 & 46.992 & 0.024 & & \\
        4 & 52.224 & 0.024 & & \\
        5 & 57.456 & 0.024 & & \\
        6 & 62.688 & 0.024 & & \\
        7 & 67.920 & 0.024 & & \\
        8 & 73.152 & 0.024 & & \\
    \enddata
\end{deluxetable*}

The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
Owens Valley Radio Observatory (OVRO) near Big Pine, California \citep{todo_hallinan_2017}.  The
OVRO-LWA is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912
MHz and 24 kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that
there are $288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA
correlator \citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible
hemisphere in a single snapshot image.  In the current configuration 32 antennas (64 signal paths)
are unused.

The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
placed outside of the core in order to extend the maximum baseline length out to $\sim$1.5 km. The
final 5 antennas are equipped with noise-switched front ends for calibrated total power measurements
of the global sky brightness.  These antennas are used as part of the LEDA experiment
\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.

Beginning at 2017-02-17 12:00:00 UTC time, 28 consecutive hours of data was collected. This time was
chosen based on the fact that it was raining at OVRO and rain tends to improve the low-frequency RFI
environment considerably. During this time the OVRO-LWA operated as a zenith-pointing drift scanning
interferometer.  The correlator dump time was selected to be 13 seconds such that the correlator
output evenly divides a sidereal day.

@@

The antenna complex gains are measured from a 22 minute track of data from when Cyg A and Cas are at
high elevations. The gains measured in this way are then used to calibrate the entire 28 hour
dataset. Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources
in the northern hemisphere. Therefore the optimal time to solve for the interferometer's gain
calibration is when these sources are at high elevations. The calibration sky model consists only of
Cyg A and Cas A. The flux of Cyg A is anchored to the results of \citet{1977A&A....61...99B} while
the flux of Cas A is measured from the data itself (using a preliminary calibration).

@@

In order to generate wide-field images of the sky, the response of the antenna to the sky must be
known. Fortunately drift-scanning interferometers like the OVRO-LWA can empirically measure their
primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
assume that the primary beam is invariant under north-south and east-west flips, and additionally
that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
antennas will contribute towards breaking these symmetries at some level. However some amount of
symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
when the flux of a source is unknown.

We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of the fitted beam
model.

@@

Without removing bright sources from the data, sidelobes from bright sources will dominate the
variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2017ApJS..230....7P}. A
conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.

@@

The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO-LWA marginally resolves both
sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
source model to eachs ource. This is performed by minimizing the minimizing the variance within an
aperture located on each source after peeling. By phasing up a large number of integrations before
imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
until the variance within the aperture is minimized.

@@

However, the ionosphere will cause these sources to scintillate and refract. So first the position
and flux of each source is measured separately in each channel and integration. Then the sources are
subtracted from the visibilities using the updated position and flux of the source. The brightest of
these sources (Vir A and Tau A) will be peeled using a direction dependent calibration when they are
at high elevations.

@@

The sun can be trivially removed from any map of the sky by constructing the map using only data
taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
sun is well-resolved by the OVRO-LWA and hence a somewhat detailed source model is needed. In fact
the optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new
model is needed for each of the 8 channel maps produced in this paper. So while we could fit a
limited number of Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.
Additionally while most astronomical sources at these frequencies have negative spectral indices,
the Sun has a large positive spectral index. Therefore more care will need to be taken in
subtracting the Sun at higher frequencies than at lower frequencies.

@@

\begin{figure*}[p]
    \gridline{
        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
    }
\end{figure*}
\begin{figure*}[p]
    \gridline{
        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
    }
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}

The flux scale of the data was anchored to the \citet{1977A&A....61...99B} spectrum of Cyg A during
gain calibration. However, gain calibration is also a function of the beam model and the spectrum
used for Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature
and \citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
with calibrated flux measurements from one (just Cyg A) to eleven in total. However while the
\citet{2012MNRAS.423L..30S} flux scale is valid between 30 MHz and 300 MHz, the
\citet{2017ApJS..230....7P} flux scale is somewhat more limited because the lowest frequency
observations come from the VLA 4-band system. As a consequence the \citet{2017ApJS..230....7P} flux
scale is not valid below 50 MHz.

Figure~\ref{fig:flux-scale} shows a comparison between flux measurements made using the all-sky maps
from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
measurements agree to better than 10\% with the \citet{2012MNRAS.423L..30S} spectra. Below 50 MHz
there can be substantial departures with respect to the \citet{2017ApJS..230....7P} spectra (for eg.
3C 286, 3C 295, and 3C 380), but it is usually the case that we have much better agreement with the
\citet{2015A&A...582A.123H} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
diverge from the truth rapidly below 50 MHz.

@@

The goal of all imaging algorithms is to estimate the brightness of the sky $I_\nu(\hat r)$ in the
direction $\hat r$ and frequency $\nu$. A radio interferometer measures the visibilities
$V_{ij,\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
are separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes their response to the
incident radiation, then
\begin{equation}\label{eq:basic-imaging}
    V^{ij}_\nu = \int_\text{sky}
                 A_\nu(\hat r) I_\nu(\hat r)
                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, .
\end{equation}
Imaging the output of a radio interferometer therefore consists of estimating $I_\nu(\hat r)$ given
the available measurements $V^{ij}_\nu$.

@@

Naively one might attempt to solve equation~\ref{eq:basic-imaging} by discretizing, and subsequently
solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations then
the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
sky is discretized into $N_\text{pix}$ pixels then the relevant matrix has dimensions of
$(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
the OVRO-LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit complex
floating point number).  This matrix equation is therefore prohibitively large, and solving
equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
\citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.

Instead it is common to make mild assumptions that simplify equation~\ref{eq:basic-imaging} and ease
the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
$\vec b_{ij}$ lie in a plane and the field-of-view is small, equation~\ref{eq:basic-imaging} can be
well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
restriction on baseline co-planarity and field-of-view can be relaxed by using W-projection
\citep{2008ISTSP...2..647C}. Known primary beam effects can also be accounted for during imaging by
using A-projection \citep{2013ApJ...770...91B}.

@@

On the other hand, transit telescopes can take advantage of a symmetry in
equation~\ref{eq:basic-imaging} that greatly reduces the amount of computer time required to image
the full-sky with exact incorporation of widefield imaging effects. This technique, called $m$-mode
analysis, also obviates the need for gridding, mosaicing, and multi-scale deconvolution. Instead the
entire sky is imaged in one coherent synthesis imaging step.

@@

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA. Compare this number with the 5 PB required for the naive approach.  The
power of $m$-mode analysis is the block-diagonal structure of
equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
the computational complexity involved in inverting the equation is reduced by a factor $N^3$. For
the case of the OVRO-LWA the equation breaks up into $\sim10^3$ blocks and so we save a factor of
$\sim10^9$ in processing time by using $m$-mode analysis.

@@

These terrestrial sources do not rotate with the sky and hence their contamination tends to be
restricted to modes with small $m$. In this dataset the contamination is largely restricted to $m
\lesssim 3$. As a result if the contamination is not suppressed, it will manifest itself as rings
along stripes of constant declination. This effect is plainly visible in Figure \todo{make it}.

@@

\todo{describe how the Wiener filter works}

>>>>

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
scattering, absorption, or additional emission can perturb the thermal CMB spectrum. In order to
measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free emission,
thermal dust emission) are a nuisance and careful modeling and removal of these components is
essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.

@@

At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
power spectrum of this perturbation is expected to be dominated by inhomogeneous heating of the IGM
at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
7$ where a detection can constrain the ionizing efficiency of early galaxies, the UV photon
mean-free-path, and the minimum halo mass that can support star formation
\citep{2015MNRAS.449.4246G}.

Current 21 cm cosmology experiments can be broadly separated into two classes: global experiments
that are aiming to detect the spectral signature of the cosmologically redshifted 21 cm transition
after averaging over the entire sky, and power spectrum experiments that incorporate angular
information to attempt to measure the 3D spatial power spectrum of cosmological 21 cm perturbations.
Ongoing global experiments include EDGES \citep{2010Natur.468..796B, 2017ApJ...835...49M}, LEDA
\citep{todo_price_2017}, BIGHORNS \citep{2015PASA...32....4S}, SCI-HI \citep{2014ApJ...782L...9V},
and SARAS 2 \citep{2017arXiv170306647S}.  Ongoing power spectrum experiments include PAPER/HERA
\citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA
\citep{2016ApJ...833..102B}.

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21 cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
\end{equation}
Therefore experiments conservatively need to achieve at least 4 orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
emission (after convolving with the instrumental response) is spectrally smooth. However the
low-frequency radio sky is composed of several components: galactic synchrotron emission, supernova
remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and radion
emission from a confusing background of radio sources.  Ideally a foreground removal strategy should
be informed by the measured spatial structure and frequency spectrum of all foreground components.
However this possibility is limited by the availability of suitable high-fidelity low-frequency sky
maps on angular scales ranging from tens of degrees to arcminutes.

The Global Sky Model (GSM) \citep{2008MNRAS.388..247D, 2017MNRAS.464.3486Z} is a data-driven
interpolation of various maps between 10 MHz and 100 GHz. However the majority of information
contained in the GSM is derived at higher frequencies where the majority of the input maps are
located.  Below 408 MHz, the interpolation is largely driven by the Haslam 408 MHz map
\citep{1981A&A...100..209H, 1982A&AS...47....1H}.  At lower frequencies, free-free absorption and
synchrotron self-absorption becomes increasingly important and hence spectral indices derived at
higher frequencies need corrections at lower frequencies.

Recently a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio point sources. Surveys that capture the diffuse emission include at 45 MHz, where
\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
Frequency Sky Survey \citet{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.

@@

\begin{deluxetable}{cCCCC}
    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
    \tablewidth{0pt}
    \tablehead{
        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} \\
        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)}
    }
    \startdata
        1 & 36.528 & 0.024 & 16.2 \\
        2 & 41.760 & 0.024 & 14.7 \\
        3 & 46.992 & 0.024 & 14.2 \\
        4 & 52.224 & 0.024 & 13.6 \\
        5 & 57.456 & 0.024 & 13.5 \\
        6 & 62.688 & 0.024 & 13.5 \\
        7 & 67.920 & 0.024 & 13.5 \\
        8 & 73.152 & 0.024 & 13.7 \\
    \enddata
\end{deluxetable}

The Owens Valley Long Wavelength Array (OVRO-LWA) is a 288-element interferometer located at the
Owens Valley Radio Observatory near Big Pine, California \citep{todo_hallinan_2017}.  The OVRO-LWA
is a low-frequency instrument with instantaneous bandwidth covering 27.384 MHz to 84.912 MHz with 24
kHz channelization.  Each antenna stand hosts two perpendicular broadband dipoles so that there are
$288\times2$ signal paths in total. These signal paths feed into the 512-input LEDA correlator
\citep{2015JAI.....450003K}, which allows the OVRO-LWA to capture the entire visible hemisphere in a
single snapshot image.  In the current configuration 32 antennas (64 signal paths) are unused.

The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
placed outside of the core in order to extend the maximum baseline length to $\sim$1.5 km. The final
5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
the global sky brightness.  These antennas are used as part of the LEDA experiment
\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.

The dataset used in this paper spans 28 consecutive hours beginning at 2017-02-17 12:00:00 UTC time.
This time was chosen based on the fact that it was raining at OVRO and rain tends to improve the
low-frequency RFI environment considerably. During this time the OVRO-LWA operated as a
zenith-pointing drift scanning interferometer.  The correlator dump time was selected to be 13
seconds such that the correlator output evenly divides a sidereal day.

@@

Cyg A and Cas A are -- by an order of magnitude -- the brightest point-like radio sources in the
northern hemisphere. Therefore the optimal time to solve for the interferometer's gain calibration
is when these sources are at high elevations.  The antenna complex gains are measured from a 22
minute track of data from when Cyg A and Cas are at high elevations. The gains measured in this way
are then used to calibrate the entire 28 hour dataset. The calibration sky model consists only of
Cyg A and Cas A. The model flux of Cyg A is set to the \citet{1977A&A....61...99B} spectrum while
the flux of Cas A is measured from the data itself (using a preliminary calibration).

@@

In order to generate wide-field images of the sky, the response of the antenna to the sky must be
known. Drift-scanning interferometers like the OVRO-LWA can empirically measure their
primary beam under a mild set of symmetry assumptions \citep{2012AJ....143...53P}. In this work we
assume that the primary beam is invariant under north-south and east-west flips, and additionally
that the $x$- and $y$-dipoles have the same response to the sky after rotating one by 90$^\circ$.
These symmetries are apparent in the antenna design, but real-world defects and coupling with nearby
antennas will contribute towards breaking these symmetries at some level. However some amount of
symmetry must be assumed in order to break the degeneracy between source flux and beam amplitude
when the flux of a source is unknown.

We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of a fitted beam
model at 36.528 MHz. This process is repeated for each frequency channel.

@@

Without removing bright sources from the data, sidelobes from bright sources will dominate the
variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{1977A&A....61...99B}. A
conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at least $-45$ dB down
from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.

@@

The largest angular scale of Cas A is $\sim$8 arcminutes, and the largest angular scale of Cyg A is
$\sim$2 arcminutes. With a $\sim10$ arcminute resolution, the OVRO-LWA marginally resolves both
sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
source model to each source. This is performed by minimizing the variance within an aperture located
on each source after peeling. By phasing up a large number of integrations before imaging (at least
1 hour) it is possible to smear out the contribution of the rest of the sky.  We then use NLopt's
Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model until the variance
within the aperture is minimized.

@@

However, the ionosphere will cause these sources to scintillate and refract. So the position and
flux of each source is measured separately in each channel and integration. The sources are then
subtracted from the visibilities using the updated position and flux of the source. The brightest of
these sources (Vir A and Tau A) will be peeled using a direction dependent calibration when they are
at high elevations.

@@

The sun can be trivially removed from any map of the sky by constructing the map using only data
taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
However the dataset used in this paper consists of 28 consecutive hours. Therefore we attempt to
suppress the contribution of the sun to the maps with the goal of suppressing its sidelobes.  The
sun is well-resolved by the OVRO-LWA and hence a detailed source model is needed. In fact the
optical depth $\tau=1$ surface of the sun changes with frequency and as a consequence a new model is
needed for each of the 8 channel maps produced in this paper. While we could fit a limited number of
Gaussian components to Cyg A and Cas A, this is insufficient for the Sun.  Additionally while most
astronomical sources at these frequencies have negative spectral indices, the Sun has a positive
spectral index. Therefore more care will need to be taken in subtracting the Sun at higher
frequencies than at lower frequencies.

@@

\begin{figure*}[p]
    \gridline{
        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
    }
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}
\begin{figure*}[p]
    \addtocounter{figure}{-1}
    \gridline{
        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
    }
    \caption{(continued)}
\end{figure*}

The flux scale of the data was tied to the \citet{1977A&A....61...99B} spectrum of Cyg A during gain
calibration. However gain calibration is also a function of the beam model and the spectrum used for
Cas A. Recent work by \citet{2012MNRAS.423L..30S} using archival date from the literature and
\citet{2017ApJS..230....7P} using the VLA has expanded the number of low-frequency radio sources
with calibrated flux measurements from one (just Cyg A) to eleven in total. While the
\citet{2012MNRAS.423L..30S} flux scale is valid between 30 MHz and 300 MHz, the
\citet{2017ApJS..230....7P} flux scale is somewhat more limited because the lowest frequency
observations come from the VLA 4-band system. As a consequence the \citet{2017ApJS..230....7P} flux
scale is not valid below 50 MHz.

Figure~\ref{fig:flux-scale} shows a comparison between flux measurements made using the all-sky maps
from this work, and spectra from the aforementioned flux scales. Generally the OVRO-LWA flux
measurements agree to better than 10\% with the \citet{2012MNRAS.423L..30S} spectra. Below 50 MHz
there can be substantial departures with respect to the \citet{2017ApJS..230....7P} spectra (for eg.
3C 286, 3C 295, and 3C 380), but it is usually the case that we have much better agreement with the
\citet{2012MNRAS.423L..30S} spectra. This indicates that the \citet{2017ApJS..230....7P} spectra can
diverge from the truth rapidly below 50 MHz.

@@

The goal of all imaging algorithms is to estimate the brightness of the sky $I_\nu(\hat r)$ in the
direction $\hat r$ and frequency $\nu$. A radio interferometer measures the visibilities
$V^{ij}_{\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
are separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes their response to the
incident radiation, then
\begin{equation}\label{eq:basic-imaging}
    V^{ij}_\nu = \int_\text{sky}
                 A_\nu(\hat r) I_\nu(\hat r)
                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, .
\end{equation}
Imaging the output of a radio interferometer therefore consists of estimating $I_\nu(\hat r)$ given
the available measurements $V^{ij}_\nu$.

@@

Naively one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing, and subsequently
solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations then
the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
sky is discretized into $N_\text{pix}$ pixels then the relevant matrix has dimensions of
$(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
the OVRO-LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit complex
floating point number).  This matrix equation is therefore prohibitively large, and solving
Equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
\citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.

Instead it is common to make mild assumptions that simplify Equation~\ref{eq:basic-imaging} and ease
the computational burden in solving for $I_\nu(\hat r)$. For example, when all of the baselines
$\vec b_{ij}$ lie in a plane and the field-of-view is small, Equation~\ref{eq:basic-imaging} can be
well-approximated by a two-dimensional Fourier transform \citep{2001isra.book.....T}. The
restriction on baseline co-planarity and field-of-view can be relaxed by using W-projection
\citep{2008ISTSP...2..647C}. Known primary beam effects can also be accounted for during imaging by
using A-projection \citep{2013ApJ...770...91B}.

@@

On the other hand, transit telescopes can take advantage of a symmetry in
Equation~\ref{eq:basic-imaging} that greatly reduces the amount of computer time required to image
the full-sky with exact incorporation of widefield imaging effects. This technique, called $m$-mode
analysis, also obviates the need for gridding and mosaicing. Instead the entire sky is imaged in one
coherent synthesis imaging step.

@@

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA. Compare this number with the 5 PB required for the naive approach.  The
power of $m$-mode analysis is the block-diagonal structure of
Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
the computational complexity involved in inverting the equation is reduced by a factor $N^3$. For
the case of the OVRO-LWA the equation breaks up into $\sim10^3$ blocks and so we save a factor of
$\sim10^9$ in processing time by using $m$-mode analysis.

@@

These terrestrial sources do not rotate with the sky and hence their contamination tends to be
restricted to modes with small $m$. In this dataset the contamination is largely restricted to $m
\lesssim 3$. As a result if the contamination is not suppressed, it will manifest itself as rings
along stripes of constant declination. This effect is plainly visible in Figure~\ref{fig:fitrfi}.

@@

%\todo{describe how the Wiener filter works}
